Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-05-01 docs/00-manuscripts/ieee/ieee-manuscript.tex
rewrite disc: effect of filters

% - Effect varies across learners -> suggest to use FS even on feature sets with p < 100?
The usefulness of filters in this study was apparent across all feature sets, even for the smallest feature set, HR.
Even though the effect of feature selection methods varied across algorithms, small to substantial improvement in predictive performance were achieved in almost all cases.
No optimal algorithm/filter/dataset setting was observed in this study, leading to the conclusion that one needs to try out various combinations of such to find the best performing one.

@@

% - PCA shows similar performance but probably requires tuning of main components -> check runtime!
The PCA approach did neither show the best or worst result when being compared to other feature-selection approaches.
It is able to reduce model fitting times substantially due to its nature of reducing the number of predictors to a minimum.
However, it also removes the possibility to conduct a post-analysis of feature importance by combining predictors into principal components, forcing users to decide upfront what they value more.
Since filter scores only need to be calculated once in a benchmark setting, the runtime advantage might in fact be negligible in practice.

>>>>

% - Effect varies across learners -> suggest to use FS even on feature sets with p < 100?
% - Filters can also have a negative impact
% - Filters are interesting for reducing runtime and improve interpretability, not only for performance
The usefulness of filters in this study varied.
While some filters were able to enhance model performances (up to 5 p.p. for RF and XGBoost), some caused a worse performance than using no filter at all \autoref{fig:filter-effects-no-filter}.
Since these negative cases were not caused by a specific filter method, one should include multiple filters in a modeling design if filters are going to be used.
While filters can improve the performance of models, they might be of more interesting in other aspects than performance: Reducing variables can reduce computational efforts in high-dimensional scenarios and might simplify interpretability of models.
Here, filters are a lot cheaper than wrapper methods due to their ability of being treated as a hyperparameter during the optimization stage.

@@

% - PCA shows similar performance but probably requires tuning of main components -> check runtime!
PCA used as a filter in this work did neither show the best nor worst result compared to other feature-selection approaches.
It was able to reduce model fitting times substantially due to its nature of reducing the number of predictors to a minimum.
However, it also removed the possibility to conduct a post-hoc analysis of feature importance by combining predictors into principal components, forcing users to decide upfront what they value more.
Since filter scores only need to be calculated once in a benchmark setting, the runtime advantage might in fact be negligible in practice.
